Title

### 2021-05-25 paper/main.tex
Changed a bit of the structure

\subsection{Umbrella Sampling}

\subsection{Well Tempered Multiple Walk Metadynamics}

@@

\subsection{Quantum Mechanics / Molecular Mechanics}

>>>>

\subsection{Free Energy Methods}

\subsubsection{Umbrella Sampling}

\subsubsection{Well-Tempered Multiple Walker Metadynamics}

@@

MD simulations were performed using the GROMOS11 \cite{Riniker_2011,
  Schmid_2012} and the NAMD 2.14 simulation packages
\cite{Phillips_2020}.
Details of the simulations will be presented separately for each program.

\subsubsection{GROMOS}

The SHAKE algorithm \cite{Ryckaert_1977} was employed to constrain all
bonds to their reference values with a relative tolerance of
$10^{-4}$, allowing for a time-step of 2 fs using the leapfrog
algorithm \cite{Hockney_1977}.
\subsubsection{NAMD}

% \subsection{Quantum Mechanics / Molecular Mechanics}
% NAMD was used for QM/MM simulations due to it's hybrid simulation
% implementation \cite{Melo_2018}
